---
title: "Short read Head 2 Head"
author: "Sam Lipworth"
date: "2023-07-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(tidyverse)
```


## Introduction

The purpose of this work is to compare Illumina data from the Oxford Genomics Centre (OGC) to that from two external providers (Novogene and Baseclear).

## Dataset and pre-processing

Ten E. coli isolates were sequenced by all three companies. Please note that I have subsampled to 50X maximum coverage to account for the fact that the total output by all three was different (and often very excessive).

## Basic stats

First let's compare basic quality metrics (%Q30 and %Q20 reads assessed using Seqkit stats). Overall Novogene seems to be the winner, OGC and Baseclear are very similar. Not that much in it though.
```{r seqkit, echo=FALSE, warning=FALSE, message=FALSE}
ogc<-read_tsv('./ogc_stats')
ogc$provider<-"ogc"
novogene<-read_tsv('./novogene_stats')
novogene$provider<-"novogene"
baseclear<-read_tsv('baseclear_stats')
baseclear$provider<-"baseclear"

stats<-rbind(ogc,novogene,baseclear)
stats$file<-str_replace_all(stats$file,'_.*','')

stats <- stats %>% group_by(file,provider) %>% 
  summarise(q30 = mean(`Q30(%)`), q20 = mean(`Q20(%)`))

ggplot(stats) +
  aes(provider, y=q30) +
   geom_boxplot() + geom_jitter() +
  theme_minimal()

ggplot(stats) +
  aes(x=file,y=q30, color=provider,group=provider) +
  geom_point() + theme_minimal()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + geom_line() +
  scale_color_brewer(palette = "Dark2")


ggplot(stats) +
  aes(x=file, y=q20, color=provider, group=provider) +
  geom_point() + geom_line() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_color_brewer(palette = "Dark2")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
